---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r, echo=FALSE}
library(fold)
```


# fold

<!-- badges: start -->
<!-- badges: end -->

The goal of the `fold` package is to allow `R` developers to work with many `R` directories within an `R` package. A considerable limitation regarding `R` packages development, is that one cannot create other directories/sub directories  (other than the `R` directory) and bind them to the package ecosystem.

Using `fold`, you can create as many directories/sub directories (**outside of your `R` directory**).

The `fold()` function will list all the `.R` scripts available outside of the `R` folder, assign their names to `.Rbuildignore` file and transfer them within the main `R` directory, giving you all the flexibility you need to organize your package into many directories/sub-directories.  

## Installation

You can install the development version of `fold` with: 

``` r
remotes::install_github("feddelegrand7/fold")
```

## Usage 

Just use `fold::fold()` before building or documenting your package and you're all set. 

## Example

Suppose that within this package, I would decide to have the following structure: 

```{r, echo=FALSE}
fs::dir_create("helper_functions")
fs::file_create("helper_functions/utilities.R")
fs::file_create("helper_functions/wrappers.R")

fs::dir_create("services")
fs::dir_create("services/api")
fs::file_create("services/api/api_functions.R")
```


```{r, echo=FALSE}
fs::dir_tree(".")
```


Running `fold::fold()`, all the external (external to the `R` folder) `.R` scripts will be moved within the `R` folder:

```{r}
fold::fold()
```

As such, I'll get now the following structure: 

```{r, echo=FALSE}
fs::dir_tree()
```

Notice, that script names that will be transferred to the `R` folder have their name prefixed with the character `DO_NOT_EDIT`. You can tweak this feature or deactivate it using the `script_name_suffix` parameter of the `fold()` function.

There's another parameter available, called `folders_to_ignore` which allows you to ignore certain directories (for example `dev` directory) when running the `fold` function.

Note also that `devtools::build()` and `devtools::document()` will only consider the scripts available within your `R` folder. 


```{r, echo=FALSE}
fs::dir_delete("helper_functions")
fs::dir_delete("services")

fs::file_delete("R/DO_NOT_EDIT_utilities.R")
fs::file_delete("R/DO_NOT_EDIT_wrappers.R")
fs::file_delete("R/DO_NOT_EDIT_api_functions.R")
```


## Code of Conduct

Please note that the fold project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.





